1-d Convex Elicitation Notes

### 2018-04-26 notes-1d/one-dim.tex
idle musings

Suppose we have a loss $\ell(r,y)$ which, for each $y$, is convex in $r$.
This induces a loss $\ell(r;p) = \E_{y\sim p} \ell(r,y)$ which is also convex in $r$ for each fixed $p$.

Define $\Gamma^p = \argmin_r \ell(r;p)$ to be the set of optimal reports for $p$, and note that it is a \textbf{set}.\footnote{I'm using slightly nonstandard notation here because I'm worried about multivalued properties.}
Define $\Gamma^r = \{p : r \in \Gamma^p\}$ to be the level set of $r$ as usual.

>>>>

Suppose we have a loss $\ell(r,y)$ which, for each $y$, is convex in $r$.
This induces a loss $\ell(r;p) = \E_{y\sim p} \ell(r,y)$ which is also convex in $r$ for each fixed $p$.
It induces a property where $\Gamma: \Delta_{\Y} \to 2^{\R}$ is
  \[ \Gamma(p) = \argmin_r \ell(r;p) \]
and write $\Gamma_r = \{p : r \in \Gamma(p) \}$.

Let $A_{\Gamma} = \{\Gamma_r : r \in \R\}$ be the collection of level sets and $B_{\Gamma} = \{\Gamma(p) : p \in \Delta_{\Y}\}$ be the collection of report sets. (For a single-valued property, $B_{\Gamma} = \{\{r\} : r \in \R\}$.

%\paragraph{(Non)-example.}
%Consider the mode on four outcomes $\{1,2,3,4\}$.
%It can in a sense be $1$-elicited, by letting $\R = [1,4]$ and loss function $\ell(r,y) = \begin{cases} 0 & y = \text{round}(r)  \\ 1  & \text{otherwise} \end{cases}$.
%
\begin{lemma}[Convex mapping, $1$d] \label{lemma:convex-map}
  Suppose $\Gamma$ is elicited by a one-dimensional convex loss function.
  Let $A \subseteq A_{\Gamma}$ be a collection of level sets that glue together into a convex set, i.e. $P = \Cup_{a \in A} a$ is convex.

  Then $\Gamma(P) = \cup_{p \in P} \Gamma(p)$ is convex.
\end{lemma}
